HMM

### 2015-12-29 paper3.Rnw
Please remove and reclone the repo, the repo is clean enough I think

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
\includegraphics[width=\maxwidth]{figures/cat1BICPLOT} \caption{Model Reduction Process via Individual based Model Adjusted BIC }\label{fig:BICred_plot}
\end{figure}

@@

\begin{knitrout}
\begin{figure}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figures/130avg} \caption{Average step length by time of day}
\end{figure}

@@

\begin{knitrout}
\begin{figure}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figures/130acf} \caption{ACF }
\end{figure}
\end{knitrout}

@@

\begin{knitrout}
\begin{figure}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figures/msd_plot-1} 
\end{figure}
\end{knitrout}

>>>>

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
\includegraphics[width=\maxwidth]{figures/cat1REDplot} \caption{Model Reduction Process via Individual based Model Adjusted BIC }\label{fig:BICred_plot}
\end{figure}

@@

\begin{knitrout}
\begin{figure}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figures/cat1avg} \caption{Average step length by time of day}
\end{figure}

@@

\begin{knitrout}
\begin{figure}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figures/cat1acf} \caption{ACF }
\end{figure}
\end{knitrout}

@@

\begin{knitrout}
\begin{figure}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figures/cat1states} 
\end{figure}
\end{knitrout}
